A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Figures

### 2020-11-28 writeUp/figures.tex
updated figures and ms

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/detinova_gambiae_daynight_range_lifespan_country.pdf}}
	\caption{\textbf{Day-night temperature range versus lifespan estimates for \textit{Anopheles gambiae s.l.}.} Points indicate the posterior mean estimates and the whiskers show 25\% and 75\% quantiles. Each blue line indicates a posterior estimate of the relationship between lifespan and temperature range; the orange line indicates the posterior median.}
	\label{fig:detinova_gambiae_daynight_range_lifespan_country}
\end{figure}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/mrr_elpd_vs_exponential_ordered.pdf}}
	\caption{\textbf{Detecting senescence in MRR studies.} Here, we consider the predictive accuracy of age-dependent models of mortality versus the exponential model by species. The predictive accuracy was determined using K-Fold cross-validation as described in SOM; the measure of accuracy presented here by the central dots is the difference in estimated expected log pointwise predictive density compared to the exponential model. The lower and upper whiskers represent the lower and upper bounds of the 95\% confidence interval in predictive accuracy. The species have been ordered so that those with the highest average predictive accuracy across all age-dependent models compared to the exponential model appear at the top. If all age-dependent models outperform the exponential, we deem this as evidence for age-dependent mortality (`+'); if a subsample of models perform better, we deem the evidence ambiguous (`?'); and if no age-dependent model exceeds the performance of the exponential, we conclude no evidence in favour of senescence (`-').}
	\label{fig:mrr_elpd}
\end{figure}

>>>>

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/detinova_gambiae_daynight_range_lifespan_country.pdf}}
	\caption{\textbf{Detinova dissection: day-night temperature range versus lifespan estimates for \textit{Anopheles gambiae s.l.}.} Points indicate the posterior mean estimates and the whiskers show 25\% and 75\% quantiles. Each blue line indicates a posterior estimate of the relationship between lifespan and temperature range; the orange line indicates the posterior median.}
	\label{fig:detinova_gambiae_daynight_range_lifespan_country}
\end{figure}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/mrr_elpd_vs_exponential_ordered.pdf}}
	\caption{\textbf{MRR: evidence for senescence.} Here, we consider the predictive accuracy of age-dependent models of mortality versus the exponential model by species. The predictive accuracy was determined using K-Fold cross-validation as described in SOM; the measure of accuracy presented here by the central dots is the difference in estimated expected log pointwise predictive density compared to the exponential model. The lower and upper whiskers represent the lower and upper bounds of the 95\% confidence interval in predictive accuracy. The species have been ordered so that those with the highest average predictive accuracy across all age-dependent models compared to the exponential model appear at the top. If all age-dependent models outperform the exponential, we deem this as evidence for age-dependent mortality (`+'); if a subsample of models perform better, we deem the evidence ambiguous (`?'); and if no age-dependent model exceeds the performance of the exponential, we conclude no evidence in favour of senescence (`-').}
	\label{fig:mrr_elpd}
\end{figure}

### 2020-11-28 writeUp/supplementary_materials.tex
updated figures and ms

\section{MRR experments}

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Aedes} & \textit{simpsoni s.l.} & 6.3 & 11.3 & 18.3 & 31.8 & 75.0 & 26.9 & 29.5 \\
		\textit{Aedes} & \textit{communis} & 10.0 & 13.2 & 15.4 & 18.2 & 24.3 & 16.2 & 5.2 \\
		\textit{Anopheles} & \textit{koliensis} & 6.7 & 10.5 & 15.2 & 24.0 & 56.5 & 21.9 & 25.2 \\
		\textit{Anopheles} & \textit{punctulatus} & 7.2 & 10.7 & 15.1 & 22.8 & 48.9 & 20.3 & 28.6 \\
		\textit{Aedes} & \textit{cantans} & 9.7 & 12.0 & 13.9 & 16.1 & 20.6 & 14.4 & 4.7 \\
		\textit{Aedes} & \textit{albopictus} & 8.0 & 10.0 & 11.6 & 13.7 & 17.7 & 12.1 & 3.4 \\
		\textit{Anopheles} & \textit{albimanus} & 5.9 & 8.6 & 11.6 & 16.9 & 35.7 & 15.2 & 18.7 \\
		\textit{Anopheles} & \textit{darlingi} & 4.9 & 7.3 & 10.2 & 16.0 & 37.5 & 14.5 & 14.8 \\
		\textit{Anopheles} & \textit{maculatus} & 5.7 & 7.9 & 10.2 & 13.7 & 24.3 & 12.2 & 8.7 \\
		\textit{Anopheles} & \textit{culicifacies s.l.} & 4.6 & 7.3 & 9.1 & 11.4 & 18.2 & 10.1 & 6.9 \\
		\textit{Anopheles} & \textit{sergenti} & 3.6 & 5.9 & 8.7 & 13.8 & 32.6 & 12.4 & 13.4 \\
		\textit{Aedes} & \textit{triseriatus} & 5.6 & 6.6 & 7.5 & 8.5 & 10.7 & 7.7 & 1.8 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 4.2 & 5.4 & 6.4 & 7.7 & 10.5 & 6.8 & 2.1 \\
		\textit{Aedes} & \textit{africanus} & 3.4 & 5.1 & 6.2 & 7.8 & 11.9 & 7.0 & 9.3 \\
		\textit{Aedes} & \textit{aegypti} & 2.8 & 4.5 & 6.2 & 8.5 & 13.9 & 7.0 & 3.8 \\
		\textit{Culex} & \textit{quinquefasciatus} & 4.3 & 5.2 & 5.9 & 7.0 & 9.4 & 6.3 & 1.8 \\
		\textit{Culex} & \textit{nigripalpus} & 3.5 & 4.6 & 5.8 & 7.5 & 11.3 & 6.4 & 3.1 \\
		\textit{Aedes} & \textit{notoscriptus} & 2.9 & 4.0 & 5.4 & 8.2 & 20.2 & 7.9 & 9.5 \\
		\textit{Culex} & \textit{pipiens} & 3.4 & 4.4 & 5.2 & 6.4 & 9.0 & 5.6 & 2.0 \\
		\textit{Anopheles} & \textit{saperoi} & 3.5 & 4.2 & 4.9 & 5.8 & 8.2 & 5.2 & 2.0 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 3.0 & 3.8 & 4.4 & 5.1 & 6.4 & 4.5 & 1.1 \\
		\textit{Aedes} & \textit{melanimon} & 3.3 & 3.9 & 4.3 & 4.8 & 5.7 & 4.4 & 1.0 \\
		\textit{Anopheles} & \textit{funestus s.l.} & 2.9 & 3.6 & 4.2 & 4.8 & 6.0 & 4.3 & 1.0 \\
		\textit{Anopheles} & \textit{lesteri} & 2.4 & 3.2 & 3.9 & 5.0 & 7.5 & 4.4 & 2.1 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 3.3 & 3.6 & 3.9 & 4.2 & 4.8 & 4.0 & 0.5 \\
		\textit{Anopheles} & \textit{pseudopunctipennis s.l.} & 2.3 & 2.9 & 3.5 & 4.3 & 6.7 & 3.8 & 1.9 \\
		\textit{Aedes} & \textit{vexans} & 1.9 & 2.3 & 2.6 & 3.0 & 4.1 & 2.8 & 1.0 \\
		\textit{Culex} & \textit{tarsalis} & 1.9 & 2.1 & 2.3 & 2.4 & 2.7 & 2.3 & 0.3 \\
		\textit{Anopheles} & \textit{vestitipennis} & 1.3 & 1.8 & 2.2 & 2.9 & 4.4 & 2.5 & 1.2 \\
		\textit{Anopheles} & \textit{albitarsis s.l.} & 1.3 & 1.6 & 1.9 & 2.2 & 2.9 & 2.0 & 1.0 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.7 & 0.9 & 1.1 & 1.2 & 1.6 & 1.1 & 1.0 \\
		\textit{Anopheles} & \textit{subpictus s.l.} & 0.4 & 0.6 & 0.8 & 1.1 & 2.4 & 1.1 & 2.6 \\
		\hline
		\textit{Aedes} & \text{} & 2.8 & 4.8 & 6.9 & 10.0 & 17.2 & 8.1 & 4.9 \\
		\textit{Anopheles} & \text{} & 1.5 & 3.0 & 5.0 & 8.4 & 17.8 & 6.8 & 6.4 \\
		\textit{Culex} & \text{} & 1.1 & 1.8 & 2.5 & 3.5 & 5.6 & 2.9 & 1.5 \\
		\hline
		\textbf{Overall} & \text{} & 1.4 & 2.8 & 4.6 & 7.5 & 15.4 & 6.0 & 5.2 \\
	\end{tabular}
	\caption{\textbf{Posterior summaries of mean unfed female mosquito lifespan from the MRR analysis.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
	\label{tab:mrr_estimated_lifespans}%
\end{table}%

@@

@@

\section{Polovodova dissection analysis}

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Anopheles} & \textit{sergentii} & 1.0 & 1.9 & 2.5 & 3.4 & 6.2 & 3.0 & 2.5 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 0.7 & 1.2 & 1.9 & 2.9 & 5.4 & 2.4 & 1.9 \\
		\textit{Culex} & \textit{thalassius} & 1.1 & 1.6 & 1.8 & 2.1 & 2.9 & 1.9 & 1.0 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 1.5 & 1.6 & 1.7 & 1.7 & 1.9 & 1.7 & 0.1 \\
		\textit{Anopheles} & \textit{minimus} & 0.7 & 1.2 & 1.7 & 2.2 & 4.1 & 2.0 & 2.2 \\
		\textit{Anopheles} & \textit{maculipennis} & 0.8 & 1.1 & 1.4 & 1.8 & 2.9 & 1.6 & 0.7 \\
		\textit{Culex} & \textit{pipiens} & 1.1 & 1.3 & 1.4 & 1.5 & 1.7 & 1.4 & 0.2 \\
		\textit{Mansonia} & \textit{uniformis} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{rivulorum} & 0.8 & 1.0 & 1.1 & 1.1 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{melas} & 0.8 & 1.0 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{culicifacies} & 0.9 & 1.0 & 1.0 & 1.1 & 1.2 & 1.0 & 0.1 \\
		\textit{Anopheles} & \textit{subpictus} & 0.6 & 0.9 & 1.0 & 1.2 & 2.1 & 1.2 & 2.0 \\
		\textit{Aedes} & \textit{aegypti} & 0.5 & 0.8 & 1.0 & 1.2 & 2.0 & 1.2 & 3.0 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 0.7 & 0.9 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{stephensi} & 0.6 & 0.8 & 1.0 & 1.1 & 1.6 & 1.0 & 0.4 \\
		\textit{Anopheles} & \textit{darlingi} & 0.7 & 0.8 & 0.9 & 1.0 & 1.3 & 1.0 & 0.2 \\
		\textit{Culex} & \textit{quinquefasciatus} & 0.4 & 0.7 & 0.9 & 1.3 & 2.2 & 1.1 & 0.6 \\
		\textit{Aedes} & \textit{polynesiensis} & 0.8 & 0.9 & 0.9 & 0.9 & 1.0 & 0.9 & 0.1 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.3 & 0.6 & 0.9 & 1.3 & 4.2 & 2.5 & 30.8 \\
		\textit{Culex} & \textit{annulirostris} & 0.5 & 0.8 & 0.9 & 1.0 & 1.4 & 0.9 & 0.5 \\
		\textit{Aedes} & \textit{samoanus} & 0.6 & 0.7 & 0.8 & 0.9 & 1.0 & 0.8 & 0.2 \\
		\textit{Aedes} & \textit{sollicitans} & 0.4 & 0.5 & 0.6 & 0.8 & 1.3 & 0.7 & 0.5 \\
		\textit{Aedes} & \textit{vexans} & 0.4 & 0.5 & 0.6 & 0.7 & 0.9 & 0.6 & 0.7 \\
		\textit{Anopheles} & \textit{cruzii} & 0.3 & 0.5 & 0.5 & 0.7 & 1.1 & 0.6 & 0.4 \\
		\textit{Anopheles} & \textit{bellator} & 0.3 & 0.4 & 0.5 & 0.6 & 1.0 & 0.6 & 1.8 \\
		\hline
		\textit{Anopheles} & \textit{} & 0.6 & 1.0 & 1.4 & 1.9 & 3.2 & 1.6 & 0.9 \\
		\textit{Mansonia} & \textit{} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Culex} & \textit{} & 0.5 & 0.8 & 1.0 & 1.4 & 2.3 & 1.2 & 0.6 \\
		\textit{Aedes} & \textit{} & 0.6 & 0.7 & 0.8 & 0.9 & 1.1 & 0.8 & 0.2 \\
		\hline
		\textbf{Overall} & \textit{} & 0.5 & 0.8 & 1.2 & 1.7 & 2.7 & 1.3 & 0.7 \\
	\end{tabular}
	\caption{\textbf{Posterior summaries of mean female mosquito lifespan in terms of gonotrophic cycles from dissection studies.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
	\label{tab:dissection_estimated_lifespans}%
\end{table}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifetimes_exponential_chron.pdf}}
	\caption{\textbf{Polovodova dissection: female mosquito mean chronological lifespan estimates.} The lifespans shown are for mosquitoes that were not fed with sugar or blood (for females) before release. The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:dissection_lifetimes_exponential_chron}
\end{figure}

>>>>

\section{Lifespan estimates}

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Aedes} & \textit{simpsoni s.l.} & 6.3 & 11.3 & 18.3 & 31.8 & 75.0 & 26.9 & 29.5 \\
		\textit{Aedes} & \textit{communis} & 10.0 & 13.2 & 15.4 & 18.2 & 24.3 & 16.2 & 5.2 \\
		\textit{Anopheles} & \textit{koliensis} & 6.7 & 10.5 & 15.2 & 24.0 & 56.5 & 21.9 & 25.2 \\
		\textit{Anopheles} & \textit{punctulatus} & 7.2 & 10.7 & 15.1 & 22.8 & 48.9 & 20.3 & 28.6 \\
		\textit{Aedes} & \textit{cantans} & 9.7 & 12.0 & 13.9 & 16.1 & 20.6 & 14.4 & 4.7 \\
		\textit{Aedes} & \textit{albopictus} & 8.0 & 10.0 & 11.6 & 13.7 & 17.7 & 12.1 & 3.4 \\
		\textit{Anopheles} & \textit{albimanus} & 5.9 & 8.6 & 11.6 & 16.9 & 35.7 & 15.2 & 18.7 \\
		\textit{Anopheles} & \textit{darlingi} & 4.9 & 7.3 & 10.2 & 16.0 & 37.5 & 14.5 & 14.8 \\
		\textit{Anopheles} & \textit{maculatus} & 5.7 & 7.9 & 10.2 & 13.7 & 24.3 & 12.2 & 8.7 \\
		\textit{Anopheles} & \textit{culicifacies s.l.} & 4.6 & 7.3 & 9.1 & 11.4 & 18.2 & 10.1 & 6.9 \\
		\textit{Anopheles} & \textit{sergenti} & 3.6 & 5.9 & 8.7 & 13.8 & 32.6 & 12.4 & 13.4 \\
		\textit{Aedes} & \textit{triseriatus} & 5.6 & 6.6 & 7.5 & 8.5 & 10.7 & 7.7 & 1.8 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 4.2 & 5.4 & 6.4 & 7.7 & 10.5 & 6.8 & 2.1 \\
		\textit{Aedes} & \textit{africanus} & 3.4 & 5.1 & 6.2 & 7.8 & 11.9 & 7.0 & 9.3 \\
		\textit{Aedes} & \textit{aegypti} & 2.8 & 4.5 & 6.2 & 8.5 & 13.9 & 7.0 & 3.8 \\
		\textit{Culex} & \textit{quinquefasciatus} & 4.3 & 5.2 & 5.9 & 7.0 & 9.4 & 6.3 & 1.8 \\
		\textit{Culex} & \textit{nigripalpus} & 3.5 & 4.6 & 5.8 & 7.5 & 11.3 & 6.4 & 3.1 \\
		\textit{Aedes} & \textit{notoscriptus} & 2.9 & 4.0 & 5.4 & 8.2 & 20.2 & 7.9 & 9.5 \\
		\textit{Culex} & \textit{pipiens} & 3.4 & 4.4 & 5.2 & 6.4 & 9.0 & 5.6 & 2.0 \\
		\textit{Anopheles} & \textit{saperoi} & 3.5 & 4.2 & 4.9 & 5.8 & 8.2 & 5.2 & 2.0 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 3.0 & 3.8 & 4.4 & 5.1 & 6.4 & 4.5 & 1.1 \\
		\textit{Aedes} & \textit{melanimon} & 3.3 & 3.9 & 4.3 & 4.8 & 5.7 & 4.4 & 1.0 \\
		\textit{Anopheles} & \textit{funestus s.l.} & 2.9 & 3.6 & 4.2 & 4.8 & 6.0 & 4.3 & 1.0 \\
		\textit{Anopheles} & \textit{lesteri} & 2.4 & 3.2 & 3.9 & 5.0 & 7.5 & 4.4 & 2.1 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 3.3 & 3.6 & 3.9 & 4.2 & 4.8 & 4.0 & 0.5 \\
		\textit{Anopheles} & \textit{pseudopunctipennis s.l.} & 2.3 & 2.9 & 3.5 & 4.3 & 6.7 & 3.8 & 1.9 \\
		\textit{Aedes} & \textit{vexans} & 1.9 & 2.3 & 2.6 & 3.0 & 4.1 & 2.8 & 1.0 \\
		\textit{Culex} & \textit{tarsalis} & 1.9 & 2.1 & 2.3 & 2.4 & 2.7 & 2.3 & 0.3 \\
		\textit{Anopheles} & \textit{vestitipennis} & 1.3 & 1.8 & 2.2 & 2.9 & 4.4 & 2.5 & 1.2 \\
		\textit{Anopheles} & \textit{albitarsis s.l.} & 1.3 & 1.6 & 1.9 & 2.2 & 2.9 & 2.0 & 1.0 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.7 & 0.9 & 1.1 & 1.2 & 1.6 & 1.1 & 1.0 \\
		\textit{Anopheles} & \textit{subpictus s.l.} & 0.4 & 0.6 & 0.8 & 1.1 & 2.4 & 1.1 & 2.6 \\
		\hline
		\textit{Aedes} & \text{} & 2.8 & 4.8 & 6.9 & 10.0 & 17.2 & 8.1 & 4.9 \\
		\textit{Anopheles} & \text{} & 1.5 & 3.0 & 5.0 & 8.4 & 17.8 & 6.8 & 6.4 \\
		\textit{Culex} & \text{} & 1.1 & 1.8 & 2.5 & 3.5 & 5.6 & 2.9 & 1.5 \\
		\hline
		\textbf{Overall} & \text{} & 1.4 & 2.8 & 4.6 & 7.5 & 15.4 & 6.0 & 5.2 \\
	\end{tabular}
	\caption{\textbf{MRR: mean unfed female mosquito lifespan estimates.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan. Units of lifespan are days.}
	\label{tab:mrr_estimated_lifespans}%
\end{table}%

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/detinova_insecticide.pdf}}
	\caption{\textbf{Detinova dissection: estimated impact of insecticide on lifespan.} The middle line in each box shows the median estimates. The left and right box whiskers show the 10\%, and 90\% posterior quantiles respectively.}
	\label{fig:detinova_insecticide}
\end{figure}

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/detinova_individual_lifespan_no_insecticide.pdf}}
	\caption{\textbf{Detinova dissection: individual time-series estimates of adult mosquito mean lifespan.} The middle line in each box shows the median estimates. The left and right box whiskers show the 25\%, and 75\% posterior quantiles respectively. Note, that a handful of observations are not shown in the plot since their estimates exceeded the reasonable range (here deemed to be up to 12 cycles).}
	\label{fig:detinova_lifespan_individual}
\end{figure}

@@

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Anopheles} & \textit{sergentii} & 1.0 & 1.9 & 2.5 & 3.4 & 6.2 & 3.0 & 2.5 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 0.7 & 1.2 & 1.9 & 2.9 & 5.4 & 2.4 & 1.9 \\
		\textit{Culex} & \textit{thalassius} & 1.1 & 1.6 & 1.8 & 2.1 & 2.9 & 1.9 & 1.0 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 1.5 & 1.6 & 1.7 & 1.7 & 1.9 & 1.7 & 0.1 \\
		\textit{Anopheles} & \textit{minimus} & 0.7 & 1.2 & 1.7 & 2.2 & 4.1 & 2.0 & 2.2 \\
		\textit{Anopheles} & \textit{maculipennis} & 0.8 & 1.1 & 1.4 & 1.8 & 2.9 & 1.6 & 0.7 \\
		\textit{Culex} & \textit{pipiens} & 1.1 & 1.3 & 1.4 & 1.5 & 1.7 & 1.4 & 0.2 \\
		\textit{Mansonia} & \textit{uniformis} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{rivulorum} & 0.8 & 1.0 & 1.1 & 1.1 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{melas} & 0.8 & 1.0 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{culicifacies} & 0.9 & 1.0 & 1.0 & 1.1 & 1.2 & 1.0 & 0.1 \\
		\textit{Anopheles} & \textit{subpictus} & 0.6 & 0.9 & 1.0 & 1.2 & 2.1 & 1.2 & 2.0 \\
		\textit{Aedes} & \textit{aegypti} & 0.5 & 0.8 & 1.0 & 1.2 & 2.0 & 1.2 & 3.0 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 0.7 & 0.9 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{stephensi} & 0.6 & 0.8 & 1.0 & 1.1 & 1.6 & 1.0 & 0.4 \\
		\textit{Anopheles} & \textit{darlingi} & 0.7 & 0.8 & 0.9 & 1.0 & 1.3 & 1.0 & 0.2 \\
		\textit{Culex} & \textit{quinquefasciatus} & 0.4 & 0.7 & 0.9 & 1.3 & 2.2 & 1.1 & 0.6 \\
		\textit{Aedes} & \textit{polynesiensis} & 0.8 & 0.9 & 0.9 & 0.9 & 1.0 & 0.9 & 0.1 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.3 & 0.6 & 0.9 & 1.3 & 4.2 & 2.5 & 30.8 \\
		\textit{Culex} & \textit{annulirostris} & 0.5 & 0.8 & 0.9 & 1.0 & 1.4 & 0.9 & 0.5 \\
		\textit{Aedes} & \textit{samoanus} & 0.6 & 0.7 & 0.8 & 0.9 & 1.0 & 0.8 & 0.2 \\
		\textit{Aedes} & \textit{sollicitans} & 0.4 & 0.5 & 0.6 & 0.8 & 1.3 & 0.7 & 0.5 \\
		\textit{Aedes} & \textit{vexans} & 0.4 & 0.5 & 0.6 & 0.7 & 0.9 & 0.6 & 0.7 \\
		\textit{Anopheles} & \textit{cruzii} & 0.3 & 0.5 & 0.5 & 0.7 & 1.1 & 0.6 & 0.4 \\
		\textit{Anopheles} & \textit{bellator} & 0.3 & 0.4 & 0.5 & 0.6 & 1.0 & 0.6 & 1.8 \\
		\hline
		\textit{Anopheles} & \textit{} & 0.6 & 1.0 & 1.4 & 1.9 & 3.2 & 1.6 & 0.9 \\
		\textit{Mansonia} & \textit{} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Culex} & \textit{} & 0.5 & 0.8 & 1.0 & 1.4 & 2.3 & 1.2 & 0.6 \\
		\textit{Aedes} & \textit{} & 0.6 & 0.7 & 0.8 & 0.9 & 1.1 & 0.8 & 0.2 \\
		\hline
		\textbf{Overall} & \textit{} & 0.5 & 0.8 & 1.2 & 1.7 & 2.7 & 1.3 & 0.7 \\
	\end{tabular}
	\caption{\textbf{Polovodova dissection: mean female mosquito lifespan in terms of gonotrophic cycles.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
	\label{tab:dissection_estimated_lifespans}%
\end{table}

@@

\begin{table}[htbp!]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} &
		\textbf{75$\%$} & \textbf{95$\%$} & \textbf{Mean} & \textbf{Std. dev.} \\
		\hline
	\textit{Anopheles} & \textit{gambiae (Form M)} & 0.9 & 1.8 & 2.6 & 3.6 & 6.7 & 3.2 & 4.6 \\
	\textit{Anopheles} & \textit{gambiae} & 0.6 & 1.1 & 1.7 & 2.7 & 5.6 & 2.2 & 2.2 \\
	\textit{Anopheles} & \textit{arabiensis} & 0.4 & 0.9 & 1.5 & 2.6 & 6.3 & 2.3 & 3.9 \\
	\textit{Anopheles} & \textit{gambiae s.l.} & 0.7 & 1.7 & 3.1 & 6.3 & 21.2 & 7.3 & 56.1 \\
	\textit{Anopheles} & \textit{moucheti} & 1.0 & 1.9 & 2.8 & 4.2 & 8.9 & 3.8 & 6.3 \\
	\textit{Anopheles} & \textit{funestus} & 0.8 & 1.6 & 2.7 & 4.4 & 10.6 & 4.0 & 10.6 \\
	\textit{Anopheles} & \textit{funestus s.l.} & 0.6 & 1.2 & 2.1 & 3.7 & 9.8 & 3.3 & 4.8 \\
	\textit{Anopheles} & \textit{nili s.l.} & 1.0 & 1.4 & 1.7 & 2.1 & 2.8 & 1.8 & 0.6 \\
	\textit{Anopheles} & \textit{subpictus s.l.} & 0.9 & 1.5 & 2.1 & 2.8 & 4.8 & 2.4 & 1.8 \\
	\textit{Anopheles} & \textit{dirus (formerly Sp. A)} & 0.5 & 1.0 & 1.5 & 2.2 & 4.2 & 1.8 &
	1.5 \\
	\textit{Anopheles} & \textit{dirus s.l.} & 0.6 & 1.2 & 2.0 & 3.1 & 7.4 & 2.9 & 6.8 \\
	\textit{Anopheles} & \textit{aconitus} & 0.5 & 1.1 & 1.8 & 2.8 & 6.3 & 2.5 & 4.7 \\
	\textit{Anopheles} & \textit{sundaicus s.l.} & 0.4 & 0.9 & 1.6 & 2.9 & 7.5 & 2.7 & 7.4 \\
	\textit{Anopheles} & \textit{minimus s.l.} & 0.5 & 1.1 & 1.6 & 2.5 & 5.8 & 2.3 & 5.6 \\
	\textit{Anopheles} & \textit{fluviatilis s.l.} & 0.4 & 0.9 & 1.4 & 2.3 & 5.1 & 2.0 & 3.0 \\
	\textit{Anopheles} & \textit{maculatus s.l.} & 0.6 & 1.0 & 1.2 & 1.6 & 2.5 & 1.4 & 0.8 \\
	\textit{Anopheles} & \textit{farauti s.l.} & 0.3 & 0.7 & 1.2 & 2.0 & 4.9 & 1.8 & 2.3 \\
	\textit{Anopheles} & \textit{annularis s.l.} & 0.3 & 0.7 & 1.2 & 2.0 & 4.7 & 1.7 & 1.9 \\
	\textit{Anopheles} & \textit{sinensis} & 0.4 & 0.8 & 1.1 & 1.7 & 3.0 & 1.4 & 1.0 \\
	\textit{Anopheles} & \textit{culicifacies s.l.} & 0.5 & 0.8 & 1.1 & 1.5 & 2.3 & 1.2 & 0.6 \\
	\textit{Anopheles} & \textit{anthropophagus (lesteri)} & 0.4 & 0.9 & 1.4 & 2.3 & 5.1 & 2.0 &
	3.0 \\
	\textit{Anopheles} & \textit{lesteri s.l.} & 0.3 & 0.6 & 1.1 & 1.9 & 4.7 & 1.7 & 2.4 \\
	\textit{Anopheles} & \textit{barbirostris s.l.} & 0.4 & 0.7 & 1.0 & 1.4 & 2.8 & 1.2 & 1.3 \\
	\textit{Anopheles} & \textit{albitarsis (formerly Sp C)} & 0.8 & 2.0 & 3.9 & 8.4 &
	32.6 & 13.3 & \text{$>$100} \\
	\textit{Anopheles} & \textit{albitarsis (formerly Sp A)} & 0.2 & 0.4 & 0.6 & 1.0 & 2.3 & 0.8
	& 0.9 \\
	\textit{Anopheles} & \textit{albitarsis (Sp. B)} & 0.1 & 0.3 & 0.6 & 0.9 & 1.9 & 0.7 & 0.8
	\\
	\textit{Anopheles} & \textit{albitarsis s.l.} & 0.4 & 0.9 & 1.5 & 3.0 & 8.3 & 2.8 & 5.8 \\
	\textit{Anopheles} & \textit{nuneztovari s.l.} & 0.3 & 0.6 & 1.1 & 1.9 & 4.4 & 1.6 & 2.3 \\
	\textit{Anopheles} & \textit{darlingi} & 0.2 & 0.7 & 1.2 & 2.4 & 6.7 & 2.2 & 4.2 \\
	\textit{Anopheles} & \textit{albimanus} & 0.2 & 0.5 & 0.9 & 1.6 & 3.6 & 1.3 & 1.6 \\
	\textit{Anopheles} & \textit{aquasalis} & 0.3 & 0.6 & 1.1 & 1.8 & 4.4 & 1.6 & 4.0 \\
	\textit{Anopheles} & \textit{aquasalis s.l.} & 0.2 & 0.4 & 0.7 & 1.0 & 2.4 & 0.9 & 1.3 \\
\end{tabular}
\caption{\textbf{Detinova dissection: mean female mosquito lifespan estimates in terms of gonotrophic cycles.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
\label{tab:detinova_lifespan_gonotrophic}%
\end{table}
